---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# trafficdatacollector

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of trafficdatacollector is to aid the field officers in traffic data collection as well as view the collected data.



## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(trafficdatacollector)
## basic example code
```

### Things to note about the package:

1. Uses `golem` to generate a package from R Shiny code. (https://github.com/ThinkR-open/golem)
2. Uses modules for effective code management. (https://shiny.rstudio.com/articles/modules.html)
3. Validation of user inputs before insertion into database using sqlInterpolate to avoid SQL injection attacks. (https://www.rdocumentation.org/packages/DBI/versions/0.5-1/topics/sqlInterpolate)
4. Uses `bs4Dash` to get the husky colors and `shinyWidgets` actionBttn.  (https://rinterface.github.io/bs4Dash/index.html, https://github.com/dreamRs/shinyWidgets)
5. Diabling buttons until all the required fields have been filled using shinyjs. (https://deanattali.com/shinyjs/)
6. Mobile-friendly user-interface except the direction counter. 

### Publicly hosted 
Shinyapps: https://cp84.shinyapps.io/trafficdatacollector/

Please note that the 'trafficdatacollector' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.

